Model_additionalAlts

### 2015-12-01 models/Model_additionalAlts.Rmd
updated params for fn call

Fit params - weight update fn()
```{r}
# fit_distr()
# -----------
# target        --> specific scalar family we're interested in (i.e. "some_all")
# numIters      --> 
# eta           --> 
# normalize     --> 
fit_distr = function(target, numIters = 100, eta=0.01,  normalize=F, alpha=1, verbose=F) {
  # Initialize to uniform
  w = rep(0.1, 5)
  # Focus on scalar 'target'
  scalar.focused = data.full.extras[data.full.extras$scale == target, ]
  # Initialize 'mid' alternative

  match.scalars = which(scalar.focused$degree == "hi1" | scalar.focused$degree == "hi2")

>>>>

Fit params - weight update fn()
```{r}
# fit_distr()
# -----------
# target        --> specific scalar family we're interested in (i.e. "some_all")
# numIters      --> number of iterations to run
# eta           --> step size
# alpha         --> alpha level for RSA?
# normalize     --> normalize in RSA?
fit_distr = function(target, numIters = 100, eta=0.01, normalize=T, alpha=1, verbose=F) {
  # Initialize to uniform
  w = rep(0.1, 5)
  # Focus on scalar 'target'
  scalar.focused = data.full.extras[data.full.extras$scale == target, ]
